Comparing Power Optimizations in the Reorder Buffer

### 2011-06-12 paper/end.tex
done?

Lastly further would could be expaned on our instruction generation.  As we 
currently generate synthetic instructions based on various profiles.  It would
be ideal to load in an actual instruction trace produced by alternative cycle 
accurate simulator.  This would

\section{Conclusions}
ending stuff

>>>>

Lastly further would could be expaned on our instruction generation.  As we 
currently generate synthetic instructions based on various profiles.  It would
be ideal to load in an actual instruction trace produced by alternative cycle 
accurate simulator.  This would provide the most accurate power modeling of for
the ROB model.

\section{Conclusion}
The ROB has become an intergral role in current superscalar procesors.
As the push for higher instruction throughput the ROB has grown in size
and complexitly.  Many new design ideas have been proposed to lower the
power usage of the ROB.  However there still lacks a scientific, fair and
accurate ways to compare and test the new designs.  We have created a 
power simulator for the ROB.  This provides insight into current designs
of the ROB.  Also the results can be used to help design the next generation
of ROB.
